\thesistitle

### 2019-07-15 sections/research.tex
Allow any variability

\subsubsection{A threshold for variability in literals, variables and method calls}
Type 2 clones allow any variability in literals, variables and method identifiers. However, this information tells a lot about the meaning of the code fragment. Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many. However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.

@@

For type 2R clones, we allow called methods to vary as long as they have the same argument types and return type (both of them should be compared using their fully qualified identifiers). An example of this is shown in figure \ref{fig:type2method}. In this example, we have two methods (\texttt{System.out.println} and \texttt{myFancyPrint}). We use the ``Extract Method'' refactoring method to extract a new method and use a parameter for to pass the used method.

@@

\subsubsection{Allow any change in method and class names}
When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances. In the previous section, variability in literals, variables and called methods would result in more parameters for the extracted method, thus indicating a detrimental effect on system design. This is not the case with the name of a method declaration and the name of a class/interface/enumeration declaration.

@@

For \textbf{type 2R} clones we allow any variation in literals, variables and method calls at this stage in the clone detection process. However, for \textit{literals} we do resolve their type in order to verify that they are of the same type. For \textit{variables} we also only verify that their types are the same (but not their names). For \textit{method calls}, we trace their declaration but only compare the fully qualified identifier for its return type and each of its arguments' types. Apart from that, we do not compare the names of method, class, interface and enum declarations.

@@

\subsubsection{Validating the type 2R variability threshold}
In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold. This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor. Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity. In this section we explain the way CloneRefactor uses to verify the type 2R variability threshold.

>>>>

\subsubsection{A threshold for variability in literals, variables and method calls}\label{sec:variabilitythreshold}
Type 2 clones allow any variability in literals, variables and method identifiers. However, this information tells a lot about the meaning of the code fragment. Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many. However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.

@@

Type 2R clones allow called methods to vary as long as they have the same argument types and return type. As with type 1R clones, these types are compared using their fully qualified identifiers. An example of this is shown in figure \ref{fig:type2method}. In this example, we have two methods (\texttt{System.out.println} and \texttt{myFancyPrint}). We use the ``Extract Method'' refactoring method to extract a new method and use a parameter to pass the used method.

@@

\subsubsection{Allow any variability in method and class names}
When refactored, some identifiers have no detrimental effect on the design if they vary between cloned instances. In the previous section, variability in literals, variables and called methods would result in more parameters for the extracted method, thus indicating a detrimental effect on system design. However, not always does a difference between fragments result in such a tradeoff.

This section explains several patterns of variability that we can allow between cloned fragements without changing the method by which the fragments can be refactored.

\paragraph{Class and method names}
The names of classes and methods describe the implementation of their body. If two classes/methods are cloned, but their names differ, one of both names should be redundant. When refactoring such clones, we can choose one instance to keep and one to remove. Such a refactoring doesn't affect maintainability in any other way than refactoring a type 1R clone would. The same is true of interface, enumeration and annotation names. Because of this, type 2R allows any variability in class, method, interface, enumeration and annotation names.

This is not the case with the name of a method declaration and the name of a class/interface/enumeration declaration.

@@

\textbf{Type 2R} clones allow any variation in literals, variables and method calls at this stage in the clone detection process. However, for \textit{literals} we do resolve their type in order to verify that they are of the same type. For \textit{variables} we also only verify that their types are the same (but not their names). For \textit{method calls}, we trace their declaration but only compare the fully qualified identifier for its return type and each of its arguments' types. Apart from that, we do not compare the names of method, class, interface and enum declarations.

@@

\subsubsection{Validating the type 2R variability threshold}
In the definition of type 2R clones (see section \ref{sec:type2r}) we described how type 2R clones work on basis of a variability threshold. This threshold, shown more formally in formula \ref{eq:type2r}, is checked by CloneRefactor. Implementing such a threshold involves some important design decisions, and has a lot of underwater complexity. In this section we explain how CloneRefactor detects type 2R clones on basis of this variability threshold.
